---
title: "Random intercept cross lagged panel models for social isolation and ADHD symptoms in childhood - sex differences"
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: flatly
    code_folding: hide
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = NA,
                      prompt = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      results = 'asis')

options(bitmapType = 'quartz') # to render fonts better
```

```{r Clear global environment, include=FALSE}
remove(list = ls())
```

```{r Load packages, include=FALSE}
library(knitr)
library(haven)
library(lavaan)
library(tidyverse)
library(dplyr) #conflicts with tidyverse for e.g. rename and row_number
```

```{r source the data file path, include=FALSE}
#source raw data directory: data_raw and data included
source("../isolation_ADHD_data_path.R")
```

```{r read in dta data file}
dat.raw <- read_dta(paste0(data.raw_path, "Katie_19Jan22.dta"))

dat <- dat.raw %>%
  select(id = atwinid,
         sampsex,
         seswq35,
         sisoem5,  # social isolation mother report
         sisoem7,
         sisoem10,
         sisoem12,
         sisoet5,  # social isolation teacher report
         sisoet7, 
         sisoet10,
         sisoet12,
         tadhdem5,  # total ADHD mother report
         tadhdem7,
         tadhdem10,
         tadhdem12,
         tadhdet5,  # total ADHD teacher report
         tadhdet7,
         tadhdet10,
         tadhdet12,
         hyem5,     # hyperactivity ADHD mother report
         hyem7,
         hyem10,
         hyem12, 
         hyet5,     # hyperactivity ADHD teacher report
         hyet7,
         hyet10,
         hyet12,
         inem5,    # inattention ADHD mother report
         inem7,
         inem10,
         inem12,
         inet5,    # inattention ADHD teacher report
         inet7,
         inet10,
         inet12
  )

colnames(dat)
```


To check for group differences in parameter estimates between girls and boys (sex), we can run the same model but test group differences in the lavaan command.

```{r recode sex variable}
dat <- dat %>%
  mutate(
    sex = 
      recode_factor(as_factor(sampsex),
        "1" = "Male",
        "2" = "Female"))

table(dat$sex)
```

***

# Unconstrained RI-CLPM 

## Mother report

### RI-CLPM - total ADHD scores

```{r specify RICLPM, class.source = 'fold-show'}
RICLPM <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdem5 + 1*tadhdem7 + 1*tadhdem10 + 1*tadhdem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdem5
  wad7 =~ 1*tadhdem7
  wad10 =~ 1*tadhdem10 
  wad12 =~ 1*tadhdem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM grouped by sex}
RICLPM.sex.fit <- lavaan(RICLPM, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPM.sex.fit.summary <- summary(RICLPM.sex.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we want to aaply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM, class.source = 'fold-show'}
RICLPM.sex2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdem5 + 1*tadhdem7 + 1*tadhdem10 + 1*tadhdem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdem5
  wad7 =~ 1*tadhdem7
  wad10 =~ 1*tadhdem10 
  wad12 =~ 1*tadhdem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1)*wad5 + c(b1, b1)*wsi5
  wsi7 ~ c(c1, c1)*wad5 + c(d1, d1)*wsi5
  wad10 ~ c(a2, a2)*wad7 + c(b2, b2)*wsi7
  wsi10 ~ c(c2, c2)*wad7 + c(d2, d2)*wsi7
  wad12 ~ c(a3, a3)*wad10 + c(b3, b3)*wsi10
  wsi12 ~ c(c3, c3)*wad10 + c(d3, d3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM.sex2 grouped by sex}
RICLPM.sex2.fit <- lavaan(RICLPM.sex2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPM.sex2.fit.summary <- summary(RICLPM.sex2.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.sex and RICLPM.sex2}
lavTestLRT(RICLPM.sex.fit, RICLPM.sex2.fit)
```

The chi-square difference test of these two nested models is non-significant (p=0.1118), which implies that the  lagged effects appear to be the **same for girls and boys.** 

### RI-CLPM - Hyperactivity ADHD scores

```{r specify RICLPM_hyp}
RICLPM_hyp <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyem5 + 1*hyem7 + 1*hyem10 + 1*hyem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyem5
  wad7 =~ 1*hyem7
  wad10 =~ 1*hyem10 
  wad12 =~ 1*hyem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_hyp grouped by sex}
RICLPM_hyp.sex.fit <- lavaan(RICLPM_hyp, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPM_hyp.sex.fit.summary <- summary(RICLPM_hyp.sex.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we want to aaply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM_hyp.sex2}
RICLPM_hyp.sex2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyem5 + 1*hyem7 + 1*hyem10 + 1*hyem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyem5
  wad7 =~ 1*hyem7
  wad10 =~ 1*hyem10 
  wad12 =~ 1*hyem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1)*wad5 + c(b1, b1)*wsi5
  wsi7 ~ c(c1, c1)*wad5 + c(d1, d1)*wsi5
  wad10 ~ c(a2, a2)*wad7 + c(b2, b2)*wsi7
  wsi10 ~ c(c2, c2)*wad7 + c(d2, d2)*wsi7
  wad12 ~ c(a3, a3)*wad10 + c(b3, b3)*wsi10
  wsi12 ~ c(c3, c3)*wad10 + c(d3, d3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_hyp.sex2 grouped by sex}
RICLPM_hyp.sex2.fit <- lavaan(RICLPM_hyp.sex2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPM_hyp.sex2.fit.summary <- summary(RICLPM_hyp.sex2.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM_hyp.sex and RICLPM_hyp.sex2}
lavTestLRT(RICLPM_hyp.sex.fit, RICLPM_hyp.sex2.fit)
```

The chi-square difference test of these two nested models is non-significant (p=0.7304), which implies that the lagged effects appear to be the **same for girls and boys.** 

### RI-CLPM - Inattention ADHD scores

```{r specify RICLPM_inat}
RICLPM_inat <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inem5 + 1*inem7 + 1*inem10 + 1*inem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*inem5
  wad7 =~ 1*inem7
  wad10 =~ 1*inem10 
  wad12 =~ 1*inem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_inat grouped by sex}
RICLPM_inat.sex.fit <- lavaan(RICLPM_inat, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPM_inat.sex.fit.summary <- summary(RICLPM_inat.sex.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPM_inat.sex.fit.summary.fit <- as.data.frame(t(as.data.frame(RICLPM_inat.sex.fit.summary$FIT)))[,c(3,4,9,10,13,14,16,17,18,19,21)]

#Table of regression coefficients and covariances - FEMALE
RICLPM_inat.sex.fit.summary.reg.female <- as.tibble(RICLPM_inat.sex.fit.summary$PE)[c(17:32),-c(4,5,6)]
#Table of regression coefficients and covariances - MALE
RICLPM_inat.sex.fit.summary.reg.male <- as.tibble(RICLPM_inat.sex.fit.summary$PE[c(86:101),-c(4,5,6)])
```

```{r specify RICLPM_inat.sex2}
RICLPM_inat.sex2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inem5 + 1*inem7 + 1*inem10 + 1*inem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*inem5
  wad7 =~ 1*inem7
  wad10 =~ 1*inem10 
  wad12 =~ 1*inem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1)*wad5 + c(b1, b1)*wsi5
  wsi7 ~ c(c1, c1)*wad5 + c(d1, d1)*wsi5
  wad10 ~ c(a2, a2)*wad7 + c(b2, b2)*wsi7
  wsi10 ~ c(c2, c2)*wad7 + c(d2, d2)*wsi7
  wad12 ~ c(a3, a3)*wad10 + c(b3, b3)*wsi10
  wsi12 ~ c(c3, c3)*wad10 + c(d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_inat.sex2 grouped by sex}
RICLPM_inat.sex2.fit <- lavaan(RICLPM_inat.sex2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPM_inat.sex2.fit.summary <- summary(RICLPM_inat.sex2.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.sex and RICLPM.sex2}
lavTestLRT(RICLPM_inat.sex.fit, RICLPM_inat.sex2.fit)
```

The chi-square difference test of these two nested models is *significant* (p=0.001605), which implies that lagged effects appear to be **different for girls and boys.** 

## Teacher report

# RI-CLPM - total ADHD scores

```{r specify RICLPMt, class.source = 'fold-show'}
RICLPMt <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdet5 + 1*tadhdet7 + 1*tadhdet10 + 1*tadhdet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdet5
  wad7 =~ 1*tadhdet7
  wad10 =~ 1*tadhdet10 
  wad12 =~ 1*tadhdet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt grouped by sex}
RICLPMt.sex.fit <- lavaan(RICLPMt, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPMt.sex.fit.summary <- summary(RICLPMt.sex.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPMt.sex.fit.summary.fit <- as.data.frame(t(as.data.frame(RICLPMt.sex.fit.summary$FIT)))[,c(3,4,9,10,13,14,16,17,18,19,21)]

#Table of regression coefficients and covariances - FEMALE
RICLPMt.sex.fit.summary.reg.female <- as.tibble(RICLPMt.sex.fit.summary$PE)[c(17:32),-c(4,5,6)]
#Table of regression coefficients and covariances - MALE
RICLPMt.sex.fit.summary.reg.male <- as.tibble(RICLPMt.sex.fit.summary$PE[c(86:101),-c(4,5,6)])
```

```{r specify RICLPMt.sex2'}
RICLPMt.sex2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdet5 + 1*tadhdet7 + 1*tadhdet10 + 1*tadhdet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdet5
  wad7 =~ 1*tadhdet7
  wad10 =~ 1*tadhdet10 
  wad12 =~ 1*tadhdet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1)*wad5 + c(b1, b1)*wsi5
  wsi7 ~ c(c1, c1)*wad5 + c(d1, d1)*wsi5
  wad10 ~ c(a2, a2)*wad7 + c(b2, b2)*wsi7
  wsi10 ~ c(c2, c2)*wad7 + c(d2, d2)*wsi7
  wad12 ~ c(a3, a3)*wad10 + c(b3, b3)*wsi10
  wsi12 ~ c(c3, c3)*wad10 + c(d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt.sex2 grouped by sex}
RICLPMt.sex2.fit <- lavaan(RICLPMt.sex2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPMt.sex2.fit.summary <- summary(RICLPMt.sex2.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.sex and RICLPM.sex2}
lavTestLRT(RICLPMt.sex.fit, RICLPMt.sex2.fit)
```

The chi-square difference test of these two nested models is *significant* (p=0.001178), which implies that lagged effects appear to be **different for girls and boys.** 

# RI-CLPM - Hyperactivity ADHD scores

```{r specify RICLPMt_hyp}
RICLPMt_hyp <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyet5 + 1*hyet7 + 1*hyet10 + 1*hyet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyet5
  wad7 =~ 1*hyet7
  wad10 =~ 1*hyet10 
  wad12 =~ 1*hyet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_hyp grouped by sex}
RICLPMt_hyp.sex.fit <- lavaan(RICLPMt_hyp, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPMt_hyp.sex.fit.summary <- summary(RICLPMt_hyp.sex.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPMt_hyp.sex.fit.summary.fit <- as.data.frame(t(as.data.frame(RICLPMt_hyp.sex.fit.summary$FIT)))[,c(3,4,9,10,13,14,16,17,18,19,21)]

#Table of regression coefficients and covariances - FEMALE
RICLPMt_hyp.sex.fit.summary.reg.female <- as.tibble(RICLPMt_hyp.sex.fit.summary$PE)[c(17:32),-c(4,5,6)]
#Table of regression coefficients and covariances - MALE
RICLPMt_hyp.sex.fit.summary.reg.male <- as.tibble(RICLPMt_hyp.sex.fit.summary$PE[c(86:101),-c(4,5,6)])
```

```{r specify RICLPMt_hyp.sex2}
RICLPMt_hyp.sex2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyet5 + 1*hyet7 + 1*hyet10 + 1*hyet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyet5
  wad7 =~ 1*hyet7
  wad10 =~ 1*hyet10 
  wad12 =~ 1*hyet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1)*wad5 + c(b1, b1)*wsi5
  wsi7 ~ c(c1, c1)*wad5 + c(d1, d1)*wsi5
  wad10 ~ c(a2, a2)*wad7 + c(b2, b2)*wsi7
  wsi10 ~ c(c2, c2)*wad7 + c(d2, d2)*wsi7
  wad12 ~ c(a3, a3)*wad10 + c(b3, b3)*wsi10
  wsi12 ~ c(c3, c3)*wad10 + c(d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_hyp.sex2 grouped by sex}
RICLPMt_hyp.sex2.fit <- lavaan(RICLPMt_hyp.sex2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPMt_hyp.sex2.fit.summary <- summary(RICLPMt_hyp.sex2.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.sex and RICLPM.sex2}
lavTestLRT(RICLPMt_hyp.sex.fit, RICLPMt_hyp.sex2.fit)
```

The chi-square difference test of these two nested models is *significant* (p=0.0000009), which implies that lagged effects appear to be **different for girls and boys.** 

# RI-CLPM - Inattention ADHD scores

```{r specify RICLPMt_inat}
RICLPMt_inat <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inet5 + 1*inet7 + 1*inet10 + 1*inet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*inet5
  wad7 =~ 1*inet7
  wad10 =~ 1*inet10 
  wad12 =~ 1*inet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_inat grouped by sex}
RICLPMt_inat.sex.fit <- lavaan(RICLPMt_inat, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPMt_inat.sex.fit.summary <- summary(RICLPMt_inat.sex.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

```{r specify RICLPMt_inat.sex2}
RICLPMt_inat.sex2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inet5 + 1*inet7 + 1*inet10 + 1*inet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*inet5
  wad7 =~ 1*inet7
  wad10 =~ 1*inet10 
  wad12 =~ 1*inet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1)*wad5 + c(b1, b1)*wsi5
  wsi7 ~ c(c1, c1)*wad5 + c(d1, d1)*wsi5
  wad10 ~ c(a2, a2)*wad7 + c(b2, b2)*wsi7
  wsi10 ~ c(c2, c2)*wad7 + c(d2, d2)*wsi7
  wad12 ~ c(a3, a3)*wad10 + c(b3, b3)*wsi10
  wsi12 ~ c(c3, c3)*wad10 + c(d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_inat.sex2 grouped by sex}
RICLPMt_inat.sex2.fit <- lavaan(RICLPMt_inat.sex2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "sex",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust") 

RICLPMt_inat.sex2.fit.summary <- summary(RICLPMt_inat.sex2.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.sex and RICLPM.sex2}
lavTestLRT(RICLPMt_inat.sex.fit, RICLPMt_inat.sex2.fit)
```

The chi-square difference test of these two nested models is *not* significant (p=0.06844), which implies that the lagged effects appear to be **the same for girls and boys.** 

***

# Constraints over time

Imposing constraints to the model can be achieved through **pre-multiplication**. It means that we have to prepend the number that we want to fix the parameter to, and an asterisk, to the parameter in the model specification. For example, `F =~ 0*x1` fixes the factor loading of item `x1` to factor `F` to 0. Using pre-multiplication we can also constrain parameters to be the same by giving them the same label. Below we specify an RI-CLPM with the following constraints: 

1) fixed auto-regressive and cross-lagged relations over time, `wx2 ~ a*wx1 + b*wy1; ...`
2) time-invariant (residual) (co-)variances in the within-person part `wx2 ~~ cov*wy2; ...`, `wx2 ~~ vx*wx2; ...`, and `wy2 ~~ vy*wy2; ...`
3) constrained grand means over time, `x1 + ... ~ mx*1` and `y1 + ... ~ my*1`

a = lag in ad
b = lag in si
c = cross lag ad->si
d = cross lag si->ad

From [Mulder and Hamaker (2021)](https://www.tandfonline.com/doi/full/10.1080/10705511.2020.1784738): We may consider testing if the lagged regression coefficients are time-invariant. This can be done by comparing the fit of a model with constrained regression coefficients (over time), with the fit of a model where these parameters are freely estimated (i.e., the unconstrained model). If this chi-square difference test is non-significant, this implies the constraints are tenable and the dynamics of the process are time-invariant. If the constraints are not tenable, this could be indicative of some kind of developmental process taking place during the time span covered by the study.

In this context, it is important to realize that the lagged regression coefficients depend critically on the time interval between the repeated measures. Hence, constraining the lagged parameters to be invariant across consecutive waves only makes sense when the time interval between the occasions is *(approximately) equal*. 

We will test the constraints based on the following steps recommended by Curran and Bauer:
1. Estimate the baseline model where all parameters are freely estimated (The basic RI-CLPM)
2. Impose equlaity constraints on one set of stabilities (within variable lags). Use LRT tests to see if he fit becomes significantly worse. 
3. Impose equality constraints on the next set of stabilities. Compare this to wither model 1 (baseline/basic) if step 2 was significant. Compare to model 2 if step 2 was non-significant. *Non-sig LRT = not significantly worse fit*
4. Repeat for first set of cross-lags
5. Repeat for second set of cross-lags

## Constraining lag in ADHD parameter (RICLPM2a)

a = lag in adhd












