---
title: "Random intercept cross lagged panel models for social isolation and ADHD symptoms in childhood - for different levels of SES"
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: flatly
    code_folding: hide
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment = NA,
                      prompt = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      results = 'asis')

options(bitmapType = 'quartz') # to render fonts better
```

```{r Clear global environment, include=FALSE}
remove(list = ls())
```

```{r Load packages, include=FALSE}
library(knitr)
library(haven)
library(lavaan)
library(tidyverse)
library(dplyr) #conflicts with tidyverse for e.g. rename and row_number
```

```{r source the data file path, include=FALSE}
#source raw data directory: data_raw and data included
source("../isolation_ADHD_data_path.R")
```

```{r read in dta data file}
dat.raw <- read_dta(paste0(data.raw_path, "Katie_19Jan22.dta"))

dat <- dat.raw %>%
  select(id = atwinid,
         sampsex,
         seswq35,
         sisoem5,  # social isolation mother report
         sisoem7,
         sisoem10,
         sisoem12,
         sisoet5,  # social isolation teacher report
         sisoet7, 
         sisoet10,
         sisoet12,
         tadhdem5,  # total ADHD mother report
         tadhdem7,
         tadhdem10,
         tadhdem12,
         tadhdet5,  # total ADHD teacher report
         tadhdet7,
         tadhdet10,
         tadhdet12,
         hyem5,     # hyperactivity ADHD mother report
         hyem7,
         hyem10,
         hyem12, 
         hyet5,     # hyperactivity ADHD teacher report
         hyet7,
         hyet10,
         hyet12,
         inem5,    # inattention ADHD mother report
         inem7,
         inem10,
         inem12,
         inet5,    # inattention ADHD teacher report
         inet7,
         inet10,
         inet12
  )

colnames(dat)
```

Functions

```{r functions}
# Table of model fit 
table.model.fit <- function(model){
  model.fit <- as.data.frame(t(as.data.frame(model$FIT))) %>%
    select(chisq, df, chisq.scaled, cfi.robust, tli.robust, aic, bic, bic2, rmsea.robust, rmsea.ci.lower.robust, rmsea.ci.upper.robust, srmr) #can only be used with "MLR" estimator
  return(model.fit)
}

# Table of regression and correlation (standardised covariance) - only constrained models have been made into tables. 
table.model.coef <- function(model, ses){
  if (ses == "Low"){
    model.coef <- as.tibble(model$PE[c(86:101),-c(4,5,6,7)])
    return(model.coef)
  } else if(ses == "Middle"){
    model.coef <- as.tibble(model$PE[c(17:32),-c(4,5,6,7)])
    return(model.coef)
  } else if(ses == "High"){
    model.coef <- as.tibble(model$PE[c(155:170),-c(4,5,6,7)])
    return(model.coef)
  } else {model.coef <- NULL}
}
```

First we need to recode SES as a factor, to show which level is which. 

```{r recode SES variable}
dat <- dat %>%
  mutate(
    SES = 
      recode_factor(as_factor(seswq35),
        "1" = "Low",
        "2" = "Middle", 
        "3" = "High"))

table(dat$SES)
```

***

# Unconstrained model SES differences 

## Mother report

### RI-CLPM - total ADHD symptoms

```{r specify RICLPM, class.source = 'fold-show'}
RICLPM <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdem5 + 1*tadhdem7 + 1*tadhdem10 + 1*tadhdem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdem5
  wad7 =~ 1*tadhdem7
  wad10 =~ 1*tadhdem10 
  wad12 =~ 1*tadhdem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPM grouped by ses}
RICLPM.ses.fit <- lavaan(RICLPM, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPM.ses.fit.summary <- summary(RICLPM.ses.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM.ses2}
RICLPM.ses2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdem5 + 1*tadhdem7 + 1*tadhdem10 + 1*tadhdem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdem5
  wad7 =~ 1*tadhdem7
  wad10 =~ 1*tadhdem10 
  wad12 =~ 1*tadhdem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1, a1)*wad5 + c(b1, b1, b1)*wsi5
  wsi7 ~ c(c1, c1, c1)*wad5 + c(d1, d1, d1)*wsi5
  wad10 ~ c(a2, a2, a2)*wad7 + c(b2, b2, b2)*wsi7
  wsi10 ~ c(c2, c2, c2)*wad7 + c(d2, d2, d2)*wsi7
  wad12 ~ c(a3, a3, a3)*wad10 + c(b3, b3, b3)*wsi10
  wsi12 ~ c(c3, c3, c3)*wad10 + c(d3, d3, d3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM.ses2 grouped by ses}
RICLPM.ses2.fit <- lavaan(RICLPM.ses2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.ses and RICLPM.ses2}
lavTestLRT(RICLPM.ses.fit, RICLPM.ses2.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.0006471), which implies that the lagged effects appear to be the **different for different levels of SES** 

### RI-CLPM - Hyperactivity ADHD scores

```{r specify RICLPM_hyp}
RICLPM_hyp <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyem5 + 1*hyem7 + 1*hyem10 + 1*hyem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyem5
  wad7 =~ 1*hyem7
  wad10 =~ 1*hyem10 
  wad12 =~ 1*hyem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_hyp grouped by ses}
RICLPM_hyp.ses.fit <- lavaan(RICLPM_hyp, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPM_hyp.ses.fit.summary <- summary(RICLPM_hyp.ses.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM_hyp.ses2}
RICLPM_hyp.ses2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyem5 + 1*hyem7 + 1*hyem10 + 1*hyem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyem5
  wad7 =~ 1*hyem7
  wad10 =~ 1*hyem10 
  wad12 =~ 1*hyem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1, a1)*wad5 + c(b1, b1, b1)*wsi5
  wsi7 ~ c(c1, c1, c1)*wad5 + c(d1, d1, d1)*wsi5
  wad10 ~ c(a2, a2, a2)*wad7 + c(b2, b2, b2)*wsi7
  wsi10 ~ c(c2, c2, c2)*wad7 + c(d2, d2, d2)*wsi7
  wad12 ~ c(a3, a3, a3)*wad10 + c(b3, b3, b3)*wsi10
  wsi12 ~ c(c3, c3, c3)*wad10 + c(d3, d3, d3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_hyp.ses2 grouped by ses}
RICLPM_hyp.ses2.fit <- lavaan(RICLPM_hyp.ses2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM_hyp.ses.fit and RICLPM_hyp.ses2.fit}
lavTestLRT(RICLPM_hyp.ses.fit, RICLPM_hyp.ses2.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.003791), which implies that the lagged effects appear to be the **different for different levels of SES** 

### RI-CLPM - Inattention ADHD scores

```{r specify RICLPM_inat}
RICLPM_inat <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inem5 + 1*inem7 + 1*inem10 + 1*inem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*inem5
  wad7 =~ 1*inem7
  wad10 =~ 1*inem10 
  wad12 =~ 1*inem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_inat grouped by ses}
RICLPM_inat.ses.fit <- lavaan(RICLPM_inat, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPM_inat.ses.fit.summary <- summary(RICLPM_inat.ses.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

```{r specify RICLPM_inat.ses2}
RICLPM_inat.ses2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inem5 + 1*inem7 + 1*inem10 + 1*inem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*inem5
  wad7 =~ 1*inem7
  wad10 =~ 1*inem10 
  wad12 =~ 1*inem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1, a1)*wad5 + c(b1, b1, b1)*wsi5
  wsi7 ~ c(c1, c1, c1)*wad5 + c(d1, d1, d1)*wsi5
  wad10 ~ c(a2, a2, a2)*wad7 + c(b2, b2, b2)*wsi7
  wsi10 ~ c(c2, c2, c2)*wad7 + c(d2, d2, d2)*wsi7
  wad12 ~ c(a3, a3, a3)*wad10 + c(b3, b3, b3)*wsi10
  wsi12 ~ c(c3, c3, c3)*wad10 + c(d3, d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_inat.ses2 grouped by ses}
RICLPM_inat.ses2.fit <- lavaan(RICLPM_inat.ses2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM_inat.ses.fit and RICLPM_inat.ses2.fit}
lavTestLRT(RICLPM_inat.ses.fit, RICLPM_inat.ses2.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.00123), which implies that the lagged effects appear to be the **different for different levels of SES** 

## Teacher report

### RI-CLPM - total ADHD scores

```{r specify RICLPMt, class.source = 'fold-show'}
RICLPMt <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdet5 + 1*tadhdet7 + 1*tadhdet10 + 1*tadhdet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdet5
  wad7 =~ 1*tadhdet7
  wad10 =~ 1*tadhdet10 
  wad12 =~ 1*tadhdet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt grouped by ses}
RICLPMt.ses.fit <- lavaan(RICLPMt, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPMt.ses.fit.summary <- summary(RICLPMt.ses.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

```{r specify RICLPMt.ses2}
RICLPMt.ses2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdet5 + 1*tadhdet7 + 1*tadhdet10 + 1*tadhdet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdet5
  wad7 =~ 1*tadhdet7
  wad10 =~ 1*tadhdet10 
  wad12 =~ 1*tadhdet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1, a1)*wad5 + c(b1, b1, b1)*wsi5
  wsi7 ~ c(c1, c1, c1)*wad5 + c(d1, d1, d1)*wsi5
  wad10 ~ c(a2, a2, a2)*wad7 + c(b2, b2, b2)*wsi7
  wsi10 ~ c(c2, c2, c2)*wad7 + c(d2, d2, d2)*wsi7
  wad12 ~ c(a3, a3, a3)*wad10 + c(b3, b3, b3)*wsi10
  wsi12 ~ c(c3, c3, c3)*wad10 + c(d3, d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt.ses2 grouped by ses}
RICLPMt.ses2.fit <- lavaan(RICLPMt.ses2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPMt.ses.fit and RICLPMt.ses2.fit}
lavTestLRT(RICLPMt.ses.fit, RICLPMt.ses2.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p<0.000001), which implies that the lagged effects appear to be the **different for different levels of SES** 

### RI-CLPM - Hyperactivity ADHD scores

```{r specify RICLPMt_hyp}
RICLPMt_hyp <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyet5 + 1*hyet7 + 1*hyet10 + 1*hyet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyet5
  wad7 =~ 1*hyet7
  wad10 =~ 1*hyet10 
  wad12 =~ 1*hyet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_hyp grouped by ses}
RICLPMt_hyp.ses.fit <- lavaan(RICLPMt_hyp, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPMt_hyp.ses.fit.summary <- summary(RICLPMt_hyp.ses.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)
```

```{r specify RICLPMt_hyp.ses2}
RICLPMt_hyp.ses2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyet5 + 1*hyet7 + 1*hyet10 + 1*hyet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyet5
  wad7 =~ 1*hyet7
  wad10 =~ 1*hyet10 
  wad12 =~ 1*hyet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1, a1)*wad5 + c(b1, b1, b1)*wsi5
  wsi7 ~ c(c1, c1, c1)*wad5 + c(d1, d1, d1)*wsi5
  wad10 ~ c(a2, a2, a2)*wad7 + c(b2, b2, b2)*wsi7
  wsi10 ~ c(c2, c2, c2)*wad7 + c(d2, d2, d2)*wsi7
  wad12 ~ c(a3, a3, a3)*wad10 + c(b3, b3, b3)*wsi10
  wsi12 ~ c(c3, c3, c3)*wad10 + c(d3, d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_hyp.ses2 grouped by ses}
RICLPMt_hyp.ses2.fit <- lavaan(RICLPMt_hyp.ses2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.ses and RICLPMt_hyp.ses2.fit}
lavTestLRT(RICLPMt_hyp.ses.fit, RICLPMt_hyp.ses2.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p<0.000001), which implies that the lagged effects appear to be the **different for different levels of SES** 

### RI-CLPM - Inattention ADHD scores

```{r specify RICLPMt_inat}
RICLPMt_inat <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inet5 + 1*inet7 + 1*inet10 + 1*inet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*inet5
  wad7 =~ 1*inet7
  wad10 =~ 1*inet10 
  wad12 =~ 1*inet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables
  wad7 + wsi7 ~ wad5 + wsi5
  wad10 + wsi10 ~ wad7 + wsi7
  wad12 + wsi12 ~ wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_inat grouped by ses}
RICLPMt_inat.ses.fit <- lavaan(RICLPMt_inat, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

```{r specify RICLPMt_inat.ses2}
RICLPMt_inat.ses2 <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inet5 + 1*inet7 + 1*inet10 + 1*inet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*inet5
  wad7 =~ 1*inet7
  wad10 =~ 1*inet10 
  wad12 =~ 1*inet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups. 
  wad7 ~ c(a1, a1, a1)*wad5 + c(b1, b1, b1)*wsi5
  wsi7 ~ c(c1, c1, c1)*wad5 + c(d1, d1, d1)*wsi5
  wad10 ~ c(a2, a2, a2)*wad7 + c(b2, b2, b2)*wsi7
  wsi10 ~ c(c2, c2, c2)*wad7 + c(d2, d2, d2)*wsi7
  wad12 ~ c(a3, a3, a3)*wad10 + c(b3, b3, b3)*wsi10
  wsi12 ~ c(c3, c3, c3)*wad10 + c(d3, d3, d3)*wsi10 
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_inat.ses2 grouped by ses}
RICLPMt_inat.ses2.fit <- lavaan(RICLPMt_inat.ses2, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPMt_inat.ses.fit and RICLPMt_inat.ses2.fit}
lavTestLRT(RICLPMt_inat.ses.fit, RICLPMt_inat.ses2.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.0001883), which implies that the lagged effects appear to be the **different for different levels of SES** 

***

# Constrained model with SES differences 

We have previously compared our freed model to the sex constraints model, showing if there are sex group differences between each freed model. Now, we will compare the sex constraints model to our with already set constrainted on the lagged parameters. Mother report will have only cross-lags constrained, and teacher report will have both cross-lags and autoregressive lags constrained across groups.

**All models showed significant sex differences in the unconstrained model, therefore all models will be tested in the constrained model. 

Imposing constraints to the model can be achieved through **pre-multiplication**. It means that we have to prepend the number that we want to fix the parameter to, and an asterisk, to the parameter in the model specification. For example, `F =~ 0*x1` fixes the factor loading of item `x1` to factor `F` to 0. Using pre-multiplication we can also constrain parameters to be the same by giving them the same label. Below we specify an RI-CLPM with the following constraints: 

Naming: 
  a = lag in ad
  b = lag in si
  c = cross lag ad->si
  d = cross lag si->ad

  sex.c = sex differences in constrained model 
  lag.c = lag constrained model
  sex.lag.c = sex and lag constrained model

We will text for sex differences in two steps: 
  1) We want to apply constraints to the lagged parameters, but allow these to vary between groups. If the chi square is significant then the lagged effects for boys and girls are different.
  2) We want to apply sex group constraints to the lag constraints from step 1, where the lagged parameters are the same across groups. If the chi square is significant then the lagged effects for boys and girls are different.

Here we want to constrain the lagged parameters to be the same. For example with lag c, I have constrained each lag to be set to c1 for females and c2 for males. They layout for group specification is c(group 1, group 2). 

## Mother report

### RI-CLPM - total ADHD symptoms

```{r specify RICLPM.lag.c, class.source = 'fold-show'}
RICLPM.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdem5 + 1*tadhdem7 + 1*tadhdem10 + 1*tadhdem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdem5
  wad7 =~ 1*tadhdem7
  wad10 =~ 1*tadhdem10 
  wad12 =~ 1*tadhdem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Constrained lagged effects between the within-person centered variables. c(group1/females, group2/males) - different values across groups, but the same values within groups and across lags. 
  wad7 ~ wad5 + c(d1,d2,d3)*wsi5 
  wsi7 ~ c(c1,c2,c3)*wad5 + wsi5
  
  wad10 ~ wad7 + c(d1,d2,d3)*wsi7
  wsi10 ~ c(c1,c2,c3)*wad7 + wsi7
  
  wad12 ~ wad10 + c(d1,d2,d3)*wsi10
  wsi12 ~ c(c1,c2,c3)*wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPM.lag.c grouped by ses}
RICLPM.lag.c.fit <- lavaan(RICLPM.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPM.lag.c.fit.summary <- summary(RICLPM.lag.c.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPM.lag.c.fit.summary.fit <- table.model.fit(RICLPM.lag.c.fit.summary)
#Table of regression coefficients and covariances for females and males separately
RICLPM.lag.c.fit.summary.reg.low <- table.model.coef(model = RICLPM.lag.c.fit.summary, ses = "Low")
RICLPM.lag.c.fit.summary.reg.mid <- table.model.coef(model = RICLPM.lag.c.fit.summary, ses = "Middle")
RICLPM.lag.c.fit.summary.reg.high <- table.model.coef(model = RICLPM.lag.c.fit.summary, ses = "High")
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM.ses.lag.c}
RICLPM.ses.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdem5 + 1*tadhdem7 + 1*tadhdem10 + 1*tadhdem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdem5
  wad7 =~ 1*tadhdem7
  wad10 =~ 1*tadhdem10 
  wad12 =~ 1*tadhdem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
 # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups AND the lagged effects between the within-person centered variables. 
  wad7 ~ c(a1,a1,a1)*wad5 + c(d,d,d)*wsi5
  wsi7 ~ c(c,c,c)*wad5 + c(b1,b1,b1)*wsi5
  
  wad10 ~ c(a2,a2,a2)*wad7 + c(d,d,d)*wsi7
  wsi10 ~ c(c,c,c)*wad7 + c(b2,b2,b2)*wsi7
  
  wad12 ~ c(a3,a3,a3)*wad10 + c(d,d,d)*wsi10
  wsi12 ~ c(c,c,c)*wad10 + c(b3,b3,b3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM.ses.lag.c grouped by ses}
RICLPM.ses.lag.c.fit <- lavaan(RICLPM.ses.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM.ses and RICLPM.ses2}
lavTestLRT(RICLPM.lag.c.fit, RICLPM.ses.lag.c.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.009818), which implies that the lagged effects appear to be the **different for different levels of SES** 
When using robust test statictics (MLR estimation and satorra.bentler.2010 LRT method) this becomes non-significant (p=0.5758)

SES differences found:
- Low SES has significant ADHD -> social isolation cross-lag (p=0.022)
- Non-significant cross-lags in middle SES. 
- Non-significant cross-lags in high SES. 
- Some differences in atuoregressive paths - but need to see what this means 

### RI-CLPM - Hyperactivity ADHD symptoms

```{r specify RICLPM_hyp.lag.c, class.source = 'fold-show'}
RICLPM_hyp.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyem5 + 1*hyem7 + 1*hyem10 + 1*hyem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyem5
  wad7 =~ 1*hyem7
  wad10 =~ 1*hyem10 
  wad12 =~ 1*hyem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Constrained lagged effects between the within-person centered variables. c(group1/females, group2/males) - different values across groups, but the same values within groups and across lags. 
  wad7 ~ wad5 + c(d1,d2,d3)*wsi5 
  wsi7 ~ c(c1,c2,c3)*wad5 + wsi5
  
  wad10 ~ wad7 + c(d1,d2,d3)*wsi7
  wsi10 ~ c(c1,c2,c3)*wad7 + wsi7
  
  wad12 ~ wad10 + c(d1,d2,d3)*wsi10
  wsi12 ~ c(c1,c2,c3)*wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPM_hyp.lag.c grouped by ses}
RICLPM_hyp.lag.c.fit <- lavaan(RICLPM_hyp.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPM_hyp.lag.c.fit.summary <- summary(RICLPM_hyp.lag.c.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPM_hyp.lag.c.fit.summary.fit <- table.model.fit(RICLPM_hyp.lag.c.fit.summary)
#Table of regression coefficients and covariances for females and males separately
RICLPM_hyp.lag.c.fit.summary.reg.low <- table.model.coef(model = RICLPM_hyp.lag.c.fit.summary, ses = "Low")
RICLPM_hyp.lag.c.fit.summary.reg.mid <- table.model.coef(model = RICLPM_hyp.lag.c.fit.summary, ses = "Middle")
RICLPM_hyp.lag.c.fit.summary.reg.high <- table.model.coef(model = RICLPM_hyp.lag.c.fit.summary, ses = "High")
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM_hyp.ses.lag.c}
RICLPM_hyp.ses.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyem5 + 1*hyem7 + 1*hyem10 + 1*hyem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyem5
  wad7 =~ 1*hyem7
  wad10 =~ 1*hyem10 
  wad12 =~ 1*hyem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
 # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups AND the lagged effects between the within-person centered variables. 
  wad7 ~ c(a1,a1,a1)*wad5 + c(d,d,d)*wsi5
  wsi7 ~ c(c,c,c)*wad5 + c(b1,b1,b1)*wsi5
  
  wad10 ~ c(a2,a2,a2)*wad7 + c(d,d,d)*wsi7
  wsi10 ~ c(c,c,c)*wad7 + c(b2,b2,b2)*wsi7
  
  wad12 ~ c(a3,a3,a3)*wad10 + c(d,d,d)*wsi10
  wsi12 ~ c(c,c,c)*wad10 + c(b3,b3,b3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_hyp.ses.lag.c grouped by ses}
RICLPM_hyp.ses.lag.c.fit <- lavaan(RICLPM_hyp.ses.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM_hyp.ses and RICLPM_hyp.ses2}
lavTestLRT(RICLPM_hyp.lag.c.fit, RICLPM_hyp.ses.lag.c.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.02456), which implies that the lagged effects appear to be the **different for different levels of SES** 

SES differences found:
- Low SES has non-sig (p=0.098) ADHD -> social isolation cross-lag 
- Non-significant cross-lags in middle and high SES. 

*Can conclude here that there are no SES differences - no differences in significance of the cross-lags*

### RI-CLPM - Inattention ADHD symptoms

```{r specify RICLPM_inat.lag.c, class.source = 'fold-show'}
RICLPM_inat.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inem5 + 1*inem7 + 1*inem10 + 1*inem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*inem5
  wad7 =~ 1*inem7
  wad10 =~ 1*inem10 
  wad12 =~ 1*inem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
  # Constrained lagged effects between the within-person centered variables. c(group1/females, group2/males) - different values across groups, but the same values within groups and across lags. 
  wad7 ~ wad5 + c(d1,d2,d3)*wsi5 
  wsi7 ~ c(c1,c2,c3)*wad5 + wsi5
  
  wad10 ~ wad7 + c(d1,d2,d3)*wsi7
  wsi10 ~ c(c1,c2,c3)*wad7 + wsi7
  
  wad12 ~ wad10 + c(d1,d2,d3)*wsi10
  wsi12 ~ c(c1,c2,c3)*wad10 + wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPM_inat.lag.c grouped by ses}
RICLPM_inat.lag.c.fit <- lavaan(RICLPM_inat.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPM_inat.lag.c.fit.summary <- summary(RICLPM_inat.lag.c.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPM_inat.lag.c.fit.summary.fit <- table.model.fit(RICLPM_inat.lag.c.fit.summary)
#Table of regression coefficients and covariances for females and males separately
RICLPM_inat.lag.c.fit.summary.reg.low <- table.model.coef(model = RICLPM_inat.lag.c.fit.summary, ses = "Low")
RICLPM_inat.lag.c.fit.summary.reg.mid <- table.model.coef(model = RICLPM_inat.lag.c.fit.summary, ses = "Middle")
RICLPM_inat.lag.c.fit.summary.reg.high <- table.model.coef(model = RICLPM_inat.lag.c.fit.summary, ses = "High")
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPM_inat.ses.lag.c}
RICLPM_inat.ses.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inem5 + 1*inem7 + 1*inem10 + 1*inem12 #x
  RIsi =~ 1*sisoem5 + 1*sisoem7 + 1*sisoem10 + 1*sisoem12 #y

  # Create within-person centered variables
  wad5 =~ 1*inem5
  wad7 =~ 1*inem7
  wad10 =~ 1*inem10 
  wad12 =~ 1*inem12
  wsi5 =~ 1*sisoem5
  wsi7 =~ 1*sisoem7
  wsi10 =~ 1*sisoem10
  wsi12 =~ 1*sisoem12
  
 # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups AND the lagged effects between the within-person centered variables. 
  wad7 ~ c(a1,a1,a1)*wad5 + c(d,d,d)*wsi5
  wsi7 ~ c(c,c,c)*wad5 + c(b1,b1,b1)*wsi5
  
  wad10 ~ c(a2,a2,a2)*wad7 + c(d,d,d)*wsi7
  wsi10 ~ c(c,c,c)*wad7 + c(b2,b2,b2)*wsi7
  
  wad12 ~ c(a3,a3,a3)*wad10 + c(d,d,d)*wsi10
  wsi12 ~ c(c,c,c)*wad10 + c(b3,b3,b3)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPM_inat.ses.lag.c grouped by ses}
RICLPM_inat.ses.lag.c.fit <- lavaan(RICLPM_inat.ses.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPM_inat.ses and RICLPM_inat.ses2}
lavTestLRT(RICLPM_inat.lag.c.fit, RICLPM_inat.ses.lag.c.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.002148), which implies that the lagged effects appear to be the **different for different levels of SES** 

SES differences found:
- Low SES has significant (p=0.006) ADHD -> social isolation cross-lag 
- Non-significant cross-lags in middle and high SES. 

*Can conclude here that there are SES differences - low SES association remains only.*

***

## Teacher report

### RI-CLPM - total ADHD symptoms

```{r specify RICLPMt.lag.c, class.source = 'fold-show'}
RICLPMt.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdet5 + 1*tadhdet7 + 1*tadhdet10 + 1*tadhdet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdet5
  wad7 =~ 1*tadhdet7
  wad10 =~ 1*tadhdet10 
  wad12 =~ 1*tadhdet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Constrained lagged effects between the within-person centered variables. c(group1/middle, group2/low, group3/high) - different values across groups, but the same values within groups and across lags (all lags constrained). 
  wad7 ~ c(a1,a2,a3)*wad5 + c(d1,d2,d3)*wsi5 
  wsi7 ~ c(c1,c2,c3)*wad5 + c(b1,b2,b3)*wsi5
  
  wad10 ~ c(a1,a2,a3)*wad7 + c(d1,d2,d3)*wsi7
  wsi10 ~ c(c1,c2,c3)*wad7 + c(b1,b2,b3)*wsi7
  
  wad12 ~ c(a1,a2,a3)*wad10 + c(d1,d2,d3)*wsi10
  wsi12 ~ c(c1,c2,c3)*wad10 + c(b1,b2,b3)*wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPMt.lag.c grouped by ses}
RICLPMt.lag.c.fit <- lavaan(RICLPMt.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPMt.lag.c.fit.summary <- summary(RICLPMt.lag.c.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPMt.lag.c.fit.summary.fit <- table.model.fit(RICLPMt.lag.c.fit.summary)
#Table of regression coefficients and covariances for females and males separately
RICLPMt.lag.c.fit.summary.reg.low <- table.model.coef(model = RICLPMt.lag.c.fit.summary, ses = "Low")
RICLPMt.lag.c.fit.summary.reg.mid <- table.model.coef(model = RICLPMt.lag.c.fit.summary, ses = "Middle")
RICLPMt.lag.c.fit.summary.reg.high <- table.model.coef(model = RICLPMt.lag.c.fit.summary, ses = "High")
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPMt.ses.lag.c}
RICLPMt.ses.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*tadhdet5 + 1*tadhdet7 + 1*tadhdet10 + 1*tadhdet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*tadhdet5
  wad7 =~ 1*tadhdet7
  wad10 =~ 1*tadhdet10 
  wad12 =~ 1*tadhdet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
 # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups AND the lagged effects between the within-person centered variables. 
  wad7 ~ c(a,a,a)*wad5 + c(d,d,d)*wsi5
  wsi7 ~ c(c,c,c)*wad5 + c(b,b,b)*wsi5
  
  wad10 ~ c(a,a,a)*wad7 + c(d,d,d)*wsi7
  wsi10 ~ c(c,c,c)*wad7 + c(b,b,b)*wsi7
  
  wad12 ~ c(a,a,a)*wad10 + c(d,d,d)*wsi10
  wsi12 ~ c(c,c,c)*wad10 + c(b,b,b)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt.ses.lag.c grouped by ses}
RICLPMt.ses.lag.c.fit <- lavaan(RICLPMt.ses.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPMt.ses and RICLPMt.ses2}
lavTestLRT(RICLPMt.lag.c.fit, RICLPMt.ses.lag.c.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.004629), which implies that the lagged effects appear to be the **different for different levels of SES** 

SES differences found:
- Low SES has non significant but close (p=0.061) ADHD -> social isolation cross-lag 
- Middle SES has significant (p=0.039) ADHD -> social isolation crosslag.
- No significant cross-lags in high SES. 

*Can conclude here that there are SES differences - middle SES association remains only (close for low SES).*

### RI-CLPM - hyperactivity ADHD symptoms

```{r specify RICLPMt_hyp.lag.c, class.source = 'fold-show'}
RICLPMt_hyp.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyet5 + 1*hyet7 + 1*hyet10 + 1*hyet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyet5
  wad7 =~ 1*hyet7
  wad10 =~ 1*hyet10 
  wad12 =~ 1*hyet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Constrained lagged effects between the within-person centered variables. c(group1/middle, group2/low, group3/high) - different values across groups, but the same values within groups and across lags (all lags constrained). 
  wad7 ~ c(a1,a2,a3)*wad5 + c(d1,d2,d3)*wsi5 
  wsi7 ~ c(c1,c2,c3)*wad5 + c(b1,b2,b3)*wsi5
  
  wad10 ~ c(a1,a2,a3)*wad7 + c(d1,d2,d3)*wsi7
  wsi10 ~ c(c1,c2,c3)*wad7 + c(b1,b2,b3)*wsi7
  
  wad12 ~ c(a1,a2,a3)*wad10 + c(d1,d2,d3)*wsi10
  wsi12 ~ c(c1,c2,c3)*wad10 + c(b1,b2,b3)*wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPMt_hyp.lag.c grouped by ses}
RICLPMt_hyp.lag.c.fit <- lavaan(RICLPMt_hyp.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPMt_hyp.lag.c.fit.summary <- summary(RICLPMt_hyp.lag.c.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPMt_hyp.lag.c.fit.summary.fit <- table.model.fit(RICLPMt_hyp.lag.c.fit.summary)
#Table of regression coefficients and covariances for females and males separately
RICLPMt_hyp.lag.c.fit.summary.reg.low <- table.model.coef(model = RICLPMt_hyp.lag.c.fit.summary, ses = "Low")
RICLPMt_hyp.lag.c.fit.summary.reg.mid <- table.model.coef(model = RICLPMt_hyp.lag.c.fit.summary, ses = "Middle")
RICLPMt_hyp.lag.c.fit.summary.reg.high <- table.model.coef(model = RICLPMt_hyp.lag.c.fit.summary, ses = "High")
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPMt_hyp.ses.lag.c}
RICLPMt_hyp.ses.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*hyet5 + 1*hyet7 + 1*hyet10 + 1*hyet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*hyet5
  wad7 =~ 1*hyet7
  wad10 =~ 1*hyet10 
  wad12 =~ 1*hyet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
 # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups AND the lagged effects between the within-person centered variables. 
  wad7 ~ c(a,a,a)*wad5 + c(d,d,d)*wsi5
  wsi7 ~ c(c,c,c)*wad5 + c(b,b,b)*wsi5
  
  wad10 ~ c(a,a,a)*wad7 + c(d,d,d)*wsi7
  wsi10 ~ c(c,c,c)*wad7 + c(b,b,b)*wsi7
  
  wad12 ~ c(a,a,a)*wad10 + c(d,d,d)*wsi10
  wsi12 ~ c(c,c,c)*wad10 + c(b,b,b)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_hyp.ses.lag.c grouped by ses}
RICLPMt_hyp.ses.lag.c.fit <- lavaan(RICLPMt_hyp.ses.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPMt_hyp.ses and RICLPMt_hyp.ses2}
lavTestLRT(RICLPMt_hyp.lag.c.fit, RICLPMt_hyp.ses.lag.c.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.001871), which implies that the lagged effects appear to be the **different for different levels of SES** 

SES differences found:
- Low SES has significant (p=0.008) ADHD -> social isolation cross-lag 
- Middle SES has significant (p=0.014) ADHD -> social isolation cross-lag.
- No significant cross-lags in high SES. 

*Can conclude here that there are SES differences - low and middle SES association remains only.*

### RI-CLPM - Inattention ADHD symptoms

```{r specify RICLPMt_inat.lag.c, class.source = 'fold-show'}
RICLPMt_inat.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inet5 + 1*inet7 + 1*inet10 + 1*inet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*inet5
  wad7 =~ 1*inet7
  wad10 =~ 1*inet10 
  wad12 =~ 1*inet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
  # Constrained lagged effects between the within-person centered variables. c(group1/middle, group2/low, group3/high) - different values across groups, but the same values within groups and across lags (all lags constrained). 
  wad7 ~ c(a1,a2,a3)*wad5 + c(d1,d2,d3)*wsi5 
  wsi7 ~ c(c1,c2,c3)*wad5 + c(b1,b2,b3)*wsi5
  
  wad10 ~ c(a1,a2,a3)*wad7 + c(d1,d2,d3)*wsi7
  wsi10 ~ c(c1,c2,c3)*wad7 + c(b1,b2,b3)*wsi7
  
  wad12 ~ c(a1,a2,a3)*wad10 + c(d1,d2,d3)*wsi10
  wsi12 ~ c(c1,c2,c3)*wad10 + c(b1,b2,b3)*wsi10
  
  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

To check for group differences in parameter estimates between different levels of SES, we specify that we are interested to group by SES.

```{r fit RICLPMt_inat.lag.c grouped by ses}
RICLPMt_inat.lag.c.fit <- lavaan(RICLPMt_inat.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 

RICLPMt_inat.lag.c.fit.summary <- summary(RICLPMt_inat.lag.c.fit, 
                                fit.measures = TRUE,
                                standardized = TRUE)

#Table of model fit 
RICLPMt_inat.lag.c.fit.summary.fit <- table.model.fit(RICLPMt_inat.lag.c.fit.summary)
#Table of regression coefficients and covariances for females and males separately
RICLPMt_inat.lag.c.fit.summary.reg.low <- table.model.coef(model = RICLPMt_inat.lag.c.fit.summary, ses = "Low")
RICLPMt_inat.lag.c.fit.summary.reg.mid <- table.model.coef(model = RICLPMt_inat.lag.c.fit.summary, ses = "Middle")
RICLPMt_inat.lag.c.fit.summary.reg.high <- table.model.coef(model = RICLPMt_inat.lag.c.fit.summary, ses = "High")
```

Now we want to apply constraints over time to test if lagged parameters are invariant across groups, if the chi square is significant then the lagged effects for boys and girls are different.  

```{r specify RICLPMt_inat.ses.lag.c}
RICLPMt_inat.ses.lag.c <- '
  # Create between components (random intercepts treated as factors here)
  RIad =~ 1*inet5 + 1*inet7 + 1*inet10 + 1*inet12 #x
  RIsi =~ 1*sisoet5 + 1*sisoet7 + 1*sisoet10 + 1*sisoet12 #y

  # Create within-person centered variables
  wad5 =~ 1*inet5
  wad7 =~ 1*inet7
  wad10 =~ 1*inet10 
  wad12 =~ 1*inet12
  wsi5 =~ 1*sisoet5
  wsi7 =~ 1*sisoet7
  wsi10 =~ 1*sisoet10
  wsi12 =~ 1*sisoet12
  
 # Estimate the lagged effects between the within-person centered variables. Constrain the autoregressive effects across groups AND the lagged effects between the within-person centered variables. 
  wad7 ~ c(a,a,a)*wad5 + c(d,d,d)*wsi5
  wsi7 ~ c(c,c,c)*wad5 + c(b,b,b)*wsi5
  
  wad10 ~ c(a,a,a)*wad7 + c(d,d,d)*wsi7
  wsi10 ~ c(c,c,c)*wad7 + c(b,b,b)*wsi7
  
  wad12 ~ c(a,a,a)*wad10 + c(d,d,d)*wsi10
  wsi12 ~ c(c,c,c)*wad10 + c(b,b,b)*wsi10 

  # Estimate the covariance between the within-person centered variables at the first wave
  wad5 ~~ wsi5 # Covariance
  
  # Estimate the covariances between the residuals of the within-person centered variables (the innovations)
  wad7 ~~ wsi7
  wad10 ~~ wsi10
  wad12 ~~ wsi12
  
  # Estimate the variance and covariance of the random intercepts
  RIad ~~ RIad
  RIsi ~~ RIsi
  RIad ~~ RIsi
  
  # Estimate the (residual) variance of the within-person centered variables.
  wad5 ~~ wad5 # Variances
  wsi5 ~~ wsi5 
  wad7 ~~ wad7 # Residual variances
  wsi7 ~~ wsi7 
  wad10 ~~ wad10 
  wsi10 ~~ wsi10 
  wad12 ~~ wad12 
  wsi12 ~~ wsi12
'
```

```{r fit RICLPMt_inat.ses.lag.c grouped by ses}
RICLPMt_inat.ses.lag.c.fit <- lavaan(RICLPMt_inat.ses.lag.c, 
                      data = dat, 
                      missing = 'ML', 
                      group = "SES",
                      meanstructure = TRUE, 
                      int.ov.free = TRUE,
                      se = "robust",
                      estimator = "MLR" #maximum likelihood with robust (Huber-White) standard errors and a scaled (Yuan-Bentler) and robust test statistic
                      ) 
```

Now we see if there is a significantly worse fit when the lagged-parameters are constrained to be equal across groups. 

```{r LRT for RICLPMt_inat.ses and RICLPMt_inat.ses2}
lavTestLRT(RICLPMt_inat.lag.c.fit, RICLPMt_inat.ses.lag.c.fit, method = "satorra.bentler.2010")
```

The chi-square difference test of these two nested models is **significant** (p=0.02542), which implies that the lagged effects appear to be the **different for different levels of SES** 

SES differences found:
- No significant cross lag associations for different levels of SES.
- Significant autoregressive cross-lags for low SES only. 

*Can conclude here that there are no SES differences in inattention cross-lags*

***
